### 2023-06-13 paper/main.tex
..

Mathematically, aliasing can be modeled as the discretization of the theoretically continuous driving functions:
Assume that a suitable parametrization $d(s,t)$ of the secondary source is given, e.g. the arc length $s = R\, \cos \phi$ in case of a circular SSD (where $\phi$ is the polar angle), or the linear position on an infinite long linear SSD.
The discretization process is given by sampling the driving function by a sampling function, consisting of a series of Dirac-deltas in the actual secondary source positions:
\begin{equation}
    d_s(s,t) = \sum_{\nu = 0}^{N_0} d(s,t) \, \delta(s - \nu \Delta s),
    \label{eq:sampling_td}
\end{equation}
where $\Delta s$ is the sampling arc length.

@@

\subsubsection{Non-symmetrical antialiasing}
As an alternative antialiasing strategy, the overlapping of the spectra can be avoided by bandlimiting the driving function spectra with a spatial band-pass filter with an arbitrary center wavenumber $k_{s,0}$ and the bandwidth of the sampling wavenumber $k_{s,\mathrm{s}} = k_{s,\mathrm{Nyq}}$.

@@

\section{Comparison with direct modal bandlimitation}

@@

\bibliographystyle{unsrt}
\bibliography{dissertation}
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

>>>>

Mathematically, aliasing can be modeled as the discretization of the theoretically continuous driving functions:
Assume that a suitable parametrization $d(s,t)$ of the secondary source is given, e.g. the arc length $s = R_0\, \cos \phi$ in case of a circular SSD (where $\phi$ is the polar angle), or the linear position on an infinite long linear SSD.
The discretization process is given by sampling the driving function by a sampling function, consisting of a series of Dirac-deltas in the actual secondary source positions:
\begin{equation}
    d_s(s,t) = \sum_{\nu = 0}^{N_0} d(s,t) \, \delta(s - \nu \Delta s),
    \label{eq:sampling_td}
\end{equation}
where $\Delta s$ is the sampling arc length.

@@

\subsubsection{Non-symmetrical antialiasing}
As an alternative antialiasing strategy, the overlapping of the spectra can be avoided by bandlimiting the driving function spectra with a spatial band-pass filter with an arbitrary center wavenumber $k_{s,0}$ and the bandwidth of the sampling wavenumber $k_{s,\mathrm{s}} = 2 k_{s,\mathrm{Nyq}}$.

@@

\section{Comparison with direct modal bandlimitation}
Finally, the performance of the proposed Local Wave Field Synthesis approach is compared with conventional LWFS implementations, based on direct modal bandlimitation.

{\color{red} A paragraph from Nara should come here about (Fiete's? and) his LWFS approaches}

@@

\bibliographystyle{unsrt}
\bibliography{dissertation}
\vspace{12pt}
